Binocular combination in the autonomic nervous system

### 2024-05-09 manuscript.Rmd
Updated authors and added automatisation of downloads from OSF (individual data download doesn't seem to work).

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Joel T. Martin$^{1,2}$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,3}$ & Daniel H. Baker$^{1,3}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: elife.csl
header-includes:
- \usepackage{caption}
---

@@

$^2$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.

$^3$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.

@@

if (processdata > 2){

@@

@@

@@

>>>>

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,4}$
 | & Daniel H. Baker$^{1,4}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: elife.csl
header-includes:
- \usepackage{caption}
---

@@

$^2$School of Psychology and Vision Sciences, Leicester, United Kingdom.

$^3$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.

$^4$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.

@@

if (processdata > 2){
  # for (participant in 1:24) {
  # 
  #     # if there is no directory for this participant's data
  #     if (!file.exists(paste0(rawdir,'P',600+participant,'_S1_annotations.csv'))){
  #       
  #        # if the tar file of this participant's data doesn't exist
  #        if (!file.exists(paste0(rawdir,'P',600+participant,'.zip'))){
  #          # download it from OSF
  #          if (!exists('osffiles')){
  #          osfnode <- '6u7db'
  #          osfproject <- osf_retrieve_node(osfnode)
  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
  #         fid <- which(osffiles$name==paste0('P',600+participant,'.zip'))
  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
  #        }
  #        
  #        # then unzip the zip file
  #        unzip(paste0(rawdir,'P',600+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
  #        
  #        # and delete the tar file to save storage space
  #        file.remove(paste0(rawdir,'P',600+participant,'.zip'))
  #     }
  #   
  #   # if there is no directory for this participant's data
  #     if (!file.exists(paste0(rawdir,'P',500+participant,'_S1_annotations.csv'))){
  #       
  #        # if the tar file of this participant's data doesn't exist
  #        if (!file.exists(paste0(rawdir,'P',500+participant,'.zip'))){
  #          # download it from OSF
  #          if (!exists('osffiles')){
  #          osfnode <- 'xkgd9'
  #          osfproject <- osf_retrieve_node(osfnode)
  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
  #         fid <- which(osffiles$name==paste0('P',500+participant,'.zip'))
  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
  #        }
  #        
  #        # then unzip the zip file
  #        unzip(paste0(rawdir,'P',500+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
  #        
  #        # and delete the tar file to save storage space
  #        file.remove(paste0(rawdir,'P',500+participant,'.zip'))
  #     }
  #   
  #   # if there is no directory for this participant's data
  #     if (!file.exists(paste0(rawdir,'P',700+participant,'_S1_annotations.csv'))){
  #       
  #        # if the tar file of this participant's data doesn't exist
  #        if (!file.exists(paste0(rawdir,'P',700+participant,'.zip'))){
  #          # download it from OSF
  #          if (!exists('osffiles')){
  #          osfnode <- 'pexyk'
  #          osfproject <- osf_retrieve_node(osfnode)
  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
  #         fid <- which(osffiles$name==paste0('P',700+participant,'.zip'))
  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
  #        }
  #        
  #        # then unzip the zip file
  #        unzip(paste0(rawdir,'P',700+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
  #        
  #        # and delete the tar file to save storage space
  #        file.remove(paste0(rawdir,'P',700+participant,'.zip'))
  #     }
  #   
  #   # if there is no directory for this participant's data
  #     if (!file.exists(paste0(rawdir,'P',300+participant,'_S1_annotations.csv'))){
  #       
  #        # if the tar file of this participant's data doesn't exist
  #        if (!file.exists(paste0(rawdir,'P',300+participant,'.zip'))){
  #          # download it from OSF
  #          if (!exists('osffiles')){
  #          osfnode <- 'k9mdq'
  #          osfproject <- osf_retrieve_node(osfnode)
  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
  #         fid <- which(osffiles$name==paste0('P',300+participant,'.zip'))
  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
  #        }
  #        
  #        # then unzip the zip file
  #        unzip(paste0(rawdir,'P',300+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
  #        
  #        # and delete the tar file to save storage space
  #        file.remove(paste0(rawdir,'P',300+participant,'.zip'))
  #     }
  # }

@@

  # if there is no directory for this participant's data
      if (!file.exists(paste0(datadir,pattern='_summary.RData'))){

         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'IndividualSummary.zip'))){
           # download it from OSF
           if (!exists('osffiles')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffiles$name==paste0('IndividualSummary.zip'))
          osf_download(osffiles[fid,],datadir,progress=TRUE)
         }

         # then unzip the zip file
         unzip(paste0(datadir,'IndividualSummary.zip'), exdir=datadir, overwrite=TRUE)

         # and delete the tar file to save storage space
         file.remove(paste0(datadir,'IndividualSummary.zip'))
         file.remove(paste0(datadir,'__MACOSX'))
      }

@@

if (!file.exists(paste0(datadir,'modeloutputLum.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('modeloutputLum.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}

if (!file.exists(paste0(datadir,'modeloutputLM.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('modeloutputLM.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}

if (!file.exists(paste0(datadir,'modeloutputMel.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('modeloutputMel.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}

if (!file.exists(paste0(datadir,'modeloutputS.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('modeloutputS.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}

@@

if (!file.exists(paste0(datadir,'AveragedataLum.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('AveragedataLum.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}

if (!file.exists(paste0(datadir,'AveragedataLM.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('AveragedataLM.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}

if (!file.exists(paste0(datadir,'AveragedataMel.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('AveragedataMel.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}

if (!file.exists(paste0(datadir,'AveragedataS.RData'))){
  if (!exists('osffiles')){
    osfnode <- '9ebtd'
    osfproject <- osf_retrieve_node(osfnode)
    osffiles <- osf_ls_files(osfproject,n_max=300)
  }
  fid <- which(osffiles$name==paste0('AveragedataS.RData'))
  osf_download(osffiles[fid,],datadir,progress=TRUE)
}
